\section{Publications in conference proceedings}

The 
papers~\cite{McNeile:2013rga,McNeile:2008sr,McNeile:2007qf,McNeile:2006wj,McNeile:2002uy,McNeile:2002en,McNeile:2001hy,McNeile:1999gk} 
were invited review
talks. 
I have written a long review article for Int.Rev.Nucl.Phys. 
on hadron spectroscopy from lattice 
QCD~\cite{McNeile:2003dy}.


\begin{thebibliography}{130}

%\cite{McNeile:2013rga}
\bibitem{McNeile:2013rga}
  C.~McNeile,
  ``Strong coupling and quark masses from lattice QCD,''
  arXiv:1306.3326 [hep-lat].
  %%CITATION = ARXIV:1306.3326;%%

%\cite{Davies:2013jv}
\bibitem{Davies:2013jv} 
  C.~T.~H.~Davies, C.~McNeile, A.~Bazavov, R.~J.~Dowdall,
  K.~Hornbostel, G.~P.~Lepage and H.~Trottier,
  ``Direct determination of strange and light quark condensates from
  full lattice QCD,''
  PoS ConfinementX {\bf }, 042 (2012)
  [arXiv:1301.7204 [hep-lat]].
  %%CITATION = ARXIV:1301.7204;%%


%\cite{Davies:2013ju}
\bibitem{Davies:2013ju} 
  C.~T.~H.~Davies, G.~C.~Donald, R.~J.~Dowdall, J.~Koponen,
  E.~Follana, K.~Hornbostel, G.~P.~Lepage and C.~McNeile,
  ``Precision tests of the J/psi from full lattice QCD: mass,
  leptonic width and radiative decay rate to etac,''
  PoS ConfinementX {\bf }, 288 (2012)
  [arXiv:1301.7203 [hep-lat]].
  %%CITATION = ARXIV:1301.7203;%%

%\cite{Gregory:2011zz}
\bibitem{Gregory:2011zz}
  E.~B.~Gregory, A.~C.~Irving, C.~McNeile and C.~M.~Richards,
  ``The eta-prime meson with staggered fermions,''
  PoS LATTICE {\bf 2011} (2011) 121.
  %%CITATION = POSCI,LATTICE2011,121;%%

%\cite{Durr:2011zz}
\bibitem{Durr:2011zz}
  S.~Durr {\it et al.}  [Budapest-Marseille-Wuppertal Collaboration],
  ``Kaon bag parameter B(K) at the physical mass point,''
  PoS LATTICE {\bf 2011} (2011) 224.
  %%CITATION = POSCI,LATTICE2011,224;%%


%\cite{Bali:2011dc}
\bibitem{Bali:2011dc}
  G.~Bali, S.~Collins, S.~Durr, Z.~Fodor, R.~Horsley, C.~Hoelbling,
  S.~D.~Katz and I.~Kanamori {\it et al.},
  ``Spectra of heavy-light and heavy-heavy mesons containing charm
  quarks, including higher spin states for $N_f=2+ 1$,''
  PoS LATTICE {\bf 2011} (2011) 135
  [arXiv:1108.6147 [hep-lat]].
  %%CITATION = ARXIV:1108.6147;%%
  %10 citations counted in INSPIRE as of 02 Jul 2013



%\cite{:2010jy}
\bibitem{:2010jy}
   Koponen {\it et al.}  [HPQCD Collaboration],
  ``Heavy-light current-current correlators,''
  arXiv:1011.1208 [hep-lat].
  %%CITATION = ARXIV:1011.1208;%%


%\cite{McNeile:2009eq}
\bibitem{McNeile:2009eq}
  C.~McNeile, C.~T.~H.~Davies, E.~Follana, K.~Hornbostel,
  G.~P.~Lepage, J.~Shigemitsu [HPQCD Collaboration],
  ``Towards precise relativistic b quarks on the lattice,''
  arXiv:0910.2921
  %%CITATION = ARXIV:0910.2921;%%

\bibitem{Davies:2008nq}
  C.~T.~H.~Davies {\it et al.}  [HPQCD Collaboration],
  ``Precision charm physics, $m_c$ and $\alpha_s$ from lattice QCD,''
  arXiv:0810.3548 [hep-lat].
  %%CITATION = ARXIV:0810.3548;%%


\bibitem{Dimopoulos:2008ee}
  P.~Dimopoulos, C.~McNeile, C.~Michael, S.~Simula and C.~Urbach  [ETM
                  Collaboration],
  ``Decay constants from twisted mass QCD,''
  arXiv:0810.1220 [hep-lat].
  %%CITATION = ARXIV:0810.1220;%%



\bibitem{Allison:2008ri}
  I.~F.~Allison {\it et al.},
  ``Matching the Bare and MSbar Charm Quark Masses Using Weak
  Coupling
  Simulations,''
  arXiv:0810.0285 [hep-lat].
  %%CITATION = ARXIV:0810.0285;%%

%\cite{Kendall:2008zz}
\bibitem{Kendall:2008zz}
  I.~D.~Kendall, C.~T.~H.~Davies, C.~McNeile, G.~P.~Lepage and
  J.~Shigemitsu
                  [HPQCD Collaboration],
  %``Precision scale determination from the upsilon spectrum,''
  PoS {\bf LATTICE2008} (2008) 223.
  %%CITATION = POSCI,LATTICE2008,223;%%



\bibitem{Gregory:2008mn}
  E.~B.~Gregory, C.~McNeile, A.~C.~Irving and C.~Richards  [UKQCD
                  Collaboration],
  ``A High Statistics Study of Flavour-Singlet Mesons with Staggered
  Fermions,''
  arXiv:0810.0136 [hep-lat].
  %%CITATION = ARXIV:0810.0136;%%

%\cite{McNeile:2008sr}
\bibitem{McNeile:2008sr}
  C.~McNeile,
  ``Lattice status of gluonia/glueballs,''
  arXiv:0809.2561 [hep-lat].
  %%CITATION = ARXIV:0809.2561;%%


%\cite{McNeile:2007qf}
\bibitem{McNeile:2007qf}
  C.~McNeile,
  ``Lattice Approach to Light Scalars,''
  arXiv:0710.2470 [hep-lat].
  %%CITATION = ARXIV:0710.2470;%%

%\cite{McNeile:2007fu}
\bibitem{McNeile:2007fu}
  C.~McNeile,
  ``Hard hadron spectroscopy,''
  arXiv:0710.0985 [hep-lat].
(Plenary talk at the lattice 2007 conference).
  %%CITATION = ARXIV:0710.0985;%%


%\cite{Gregory:2007ce}
\bibitem{Gregory:2007ce}
  E.~B.~Gregory, A.~Irving, C.~M.~Richards, C.~McNeile and A.~Hart,
  ``Pseudoscalar Flavor-Singlet Physics with Staggered Fermions,''
  arXiv:0710.1725 [hep-lat].
  %%CITATION = ARXIV:0710.1725;%%

%\cite{Jansen:2007sr}
\bibitem{Jansen:2007sr}
  K.~Jansen, C.~McNeile, I.~Montvay, C.~Richard, E.~E.~Scholz, C.~Urbach and U.~Wenger,
  ``Stout Smearing for Twisted Mass Fermions,''
  PoS {\bf LATTICE2007} (2007) 036
  [arXiv:0709.4434 [hep-lat]].
  %%CITATION = POSCI,LATTICE2007,036;%%

%\cite{McNeile:2006wj}
\bibitem{McNeile:2006wj}
  C.~McNeile,
  ``Lattice approach to threshold states,''
  arXiv:hep-ph/0610139.
  %%CITATION = HEP-PH 0610139;%%

%\cite{Gregory:2006wk}
\bibitem{Gregory:2006wk}
  E.~B.~Gregory, A.~C.~Irving, C.~M.~Richards and C.~McNeile,
  ``Pseudoscalar flavor-singlets and staggered fermions,''
  arXiv:hep-lat/0610044.
  %%CITATION = HEP-LAT 0610044;%%

%\cite{Gregory:2005ms}
\bibitem{Gregory:2005ms}
E.~B.~Gregory, A.~C.~Irving, C.~McNeile, S.~Miller and Z.~Sroczynski,
``Matrix elements and baryon spectroscopy from unquenched lattice QCD
with improved staggered quarks,''
PoS {\bf LAT2005} (2005) 042
[arXiv:hep-lat/0511048].
%%CITATION = HEP-LAT 0511048;%%

%%\cite{Gregory:2005vy}
\bibitem{Gregory:2005vy}
E.~B.~Gregory, A.~Irving, C.~McNeile, S.~Miller and Z.~Sroczynski,
``Towards measuring the eta' mass with $N_f$ = 2+1 staggered
fermions,''
arXiv:hep-lat/0511038.
%%CITATION = HEP-LAT 0511038;%%

%\cite{Gregory:2005yr}
\bibitem{Gregory:2005yr}
E.~B.~Gregory, A.~C.~Irving, C.~McNeile, S.~Miller and
Z.~Sroczynski,
``Scalar glueball and meson spectroscopy in unquenched lattice QCD
with
improved staggered quarks,''
PoS {\bf LAT2005} (2005) 027
[arXiv:hep-lat/0510066].
%%CITATION = HEP-LAT 0510066;%%

%\cite{Gregory:2005me}
\bibitem{Gregory:2005me}
E.~B.~Gregory, A.~C.~Irving, C.~McNeile, S.~Miller and Z.~Sroczynski,
``Pseudoscalar singlet physics with staggered fermions,''
PoS {\bf LAT2005} (2005) 083
[arXiv:hep-lat/0509193].
%%CITATION = HEP-LAT 0509193;%%

%\cite{Green:2005st}
\bibitem{Green:2005st}
A.~M.~Green, J.~Ignatius, M.~Jahma, J.~Koponen, C.~McNeile and
C.~Michael
                  [UKQCD Collaboration],
``B/s meson excited states from the lattice,''
PoS {\bf LAT2005} (2005) 205
[arXiv:hep-lat/0509161].
%%CITATION = HEP-LAT 0509161;%%


%\cite{McNeile:2004id}
\bibitem{McNeile:2004id}
C.~McNeile, C.~Michael and G.~Thompson  [UKQCD Collaboration],
``Phenomenology of static-light mesons from unquenched lattice QCD
calculations,''
arXiv:hep-lat/0409095.
%%CITATION = HEP-LAT 0409095;%%



%\cite{Dougall:2004hx}
\bibitem{Dougall:2004hx}
A.~Dougall, C.~M.~Maynard and C.~McNeile  [UKQCD Collaboration],
``The charm quark mass with dynamical fermions,''
arXiv:hep-lat/0409089.
%%CITATION = HEP-LAT 0409089;%%


%\cite{Dougall:2003mx}
\bibitem{Dougall:2003mx}
A.~Dougall, C.~M.~Maynard and C.~McNeile  [UKQCD Collaboration],
``The mass of the charm quark from unquenched lattice QCD at fixed
lattice spacing,''
arXiv:hep-lat/0309081.
%%CITATION = HEP-LAT 0309081;%%



%\cite{Michael:2003mp}
\bibitem{Michael:2003mp}
C.~Michael and C.~McNeile  [UKQCD Collaboration],
``Hadronic decays from the lattice,''
arXiv:hep-lat/0309073.
%%CITATION = HEP-LAT 0309073;%%


%\cite{Bernard:2003gu}
\bibitem{Bernard:2003gu}
C.~Bernard {\it et al.},
``Quark loop effects in semileptonic form factors for heavy-light
mesons,''
arXiv:hep-lat/0309055.
%%CITATION = HEP-LAT 0309055;%%



%\cite{McNeile:2003dy}
\bibitem{McNeile:2003dy}
C.~McNeile,
``Meson and baryon spectroscopy on a lattice,''
arXiv:hep-lat/0307027.
 In *Green, A.M. (ed.): Hadronic physics from lattice QCD* 1-101.
Published in Int.Rev.Nucl.Phys. 
%%CITATION = HEP-LAT 0307027;%%



%\cite{McNeile:2002uy}
\bibitem{McNeile:2002uy}
C.~McNeile,
``Heavy quarks on the lattice,''
Lectures given at International School on Heavy Quark Physics, Dubna,
Russia, 27 May - 5
Jun 2002.
Lect.\ Notes Phys.\  {\bf 647} (2004) 100
arXiv:hep-lat/0210026.
%

%\cite{Hart:2002sp}
\bibitem{Hart:2002sp}
A.~Hart, C.~McNeile, and C.~Michael  [UKQCD Collaboration],
``Masses of singlet and non-singlet 0++ particles,''
arXiv:hep-lat/0209063.
%%CITATION = HEP-LAT 0209063;%%

%\cite{McNeile:2002en}
\bibitem{McNeile:2002en}
C.~McNeile,
``Lattice predictions for hybrids and glueballs,''
Nucl.\ Phys.\ A {\bf 711} (2002) 303
[arXiv:hep-lat/0207001].
%%C


%\cite{Michael:2002bv}
\bibitem{Michael:2002bv}
C.~Michael, C.~McNeile and D.~Hepburn  [UKQCD Collaboration],
``The strangeness content of the nucleon,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 106} (2002) 293
[arXiv:hep-lat/0109028].
%%CITATION = HEP-LAT 0109028;%%


%\cite{McNeile:2002yk}
\bibitem{McNeile:2002yk}
C.~McNeile and C.~Michael  [UKQCD Collaboration],
``Hadron spectroscopy of twisted mass lattice QCD at beta = 6.0,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 106} (2002) 251
[arXiv:hep-lat/0110108].
%%CITATION = HEP-LAT 0110108;%%


%\cite{Bernard:2001ht}
\bibitem{Bernard:2001ht}
C.~W.~Bernard {\it et al.},
``f(B) for various actions: Approaching the continuum limit with  dynamical fermions,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 94} (2001) 346
[arXiv:hep-lat/0011029].
%%CITATION = HEP-LAT 0011029;%%


%\cite{McNeile:2001hy}
\bibitem{McNeile:2001hy}
C.~McNeile,
``Do we understand the unquenched value of f(B)?,''
J.\ Phys.\ G {\bf 27} (2001) 1255
[arXiv:hep-lat/0012008].
%%CITATION = HEP-LAT 0012008;%%


%\cite{McNeile:2000qm}
\bibitem{McNeile:2000qm}
C.~McNeile  [UKQCD Collaboration],
``Data storage issues in lattice QCD calculations,''
arXiv:hep-lat/0003009.
%%CITATION = HEP-LAT 0003009;%%

%\cite{McNeile:2000ya}
\bibitem{McNeile:2000ya}
C.~McNeile  [UKQCD Collaboration],
``Techniques for using the overlap-Dirac operator to calculate hadron  spectroscopy,''
Chin.\ J.\ Phys.\  {\bf 38} (2000) 615
[arXiv:hep-lat/9912033].
%%CITATION = HEP-LAT 9912033;%%

%\cite{Michael:2000rs}
\bibitem{Michael:2000rs}
C.~Michael, M.~S.~Foster and C.~McNeile  [UKQCD collaboration],
``Flavour-singlet pseudoscalar and scalar mesons,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 83} (2000) 185
[arXiv:hep-lat/9909036].
%%CITATION = HEP-LAT 9909036;%%

%\cite{McNeile:2000zy}
\bibitem{McNeile:2000zy}
C.~McNeile, A.~Irving and C.~Michael  [UKQCD collaboration],
``Feasibility study of using the overlap-Dirac operator for hadron  spectroscopy,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 83} (2000) 639
[arXiv:hep-lat/9909059].
%%CITATION = HEP-LAT 9909059;%%

%\cite{Bernard:2000ic}
\bibitem{Bernard:2000ic}
C.~W.~Bernard {\it et al.},
``Semileptonic decays of heavy mesons with the fat clover action,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 83} (2000) 274
[arXiv:hep-lat/9909076].
%%CITATION = HEP-LAT 9909076;%%

%\cite{Bernard:2000nv}
\bibitem{Bernard:2000nv}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Heavy-light decay constants with dynamical gauge configurations and  Wilson or improved valence quark actions,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 83} (2000) 289
[arXiv:hep-lat/9909121].
%%CITATION = HEP-LAT 9909121;%%

%\cite{McNeile:1999gk}
\bibitem{McNeile:1999gk}
C.~McNeile,
``Latest results from lattice QCD for exotic hybrid mesons,''
arXiv:hep-lat/9904013.
%%CITATION = HEP-LAT 9904013;%%



%\cite{McNeile:1999cp}
\bibitem{McNeile:1999cp}
C.~McNeile {\it et al.},
``Exotic meson spectroscopy from the clover action at beta = 5.85 and  6.15,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 73} (1999) 264
[arXiv:hep-lat/9809087].
%%CITATION = HEP-LAT 9809087;%%

%\cite{Bernard:1999gr}
\bibitem{Bernard:1999gr}
C.~W.~Bernard {\it et al.},
``Heavy-light decay constants: Conclusions from the Wilson action,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 73} (1999) 372
[arXiv:hep-lat/9809109].
%%CITATION = HEP-LAT 9809109;%%

%\cite{Bernard:1999ni}
\bibitem{Bernard:1999ni}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Light hadron spectrum with Kogut-Susskind quarks,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 73} (1999) 198
[arXiv:hep-lat/9810035].
%%CITATION = HEP-LAT 9810035;%%



%\cite{Bernard:1998gc}
\bibitem{Bernard:1998gc}
C.~W.~Bernard {\it et al.},
``Hybrid mesons in quenched lattice QCD,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 60A} (1998) 61.
%%CITATION = NUPHZ,60A,61;%%

%\cite{Bernard:1998gm}
\bibitem{Bernard:1998gm}
C.~W.~Bernard {\it et al.},
``Towards the QCD spectrum with dynamical quarks,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 60A} (1998) 297.
%%CITATION = NUPHZ,60A,297;%%


%\cite{Bernard:1998rd}
\bibitem{Bernard:1998rd}
C.~W.~Bernard {\it et al.},
``B meson form factors from HQET simulations,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 63} (1998) 374
[arXiv:hep-lat/9709134].
%%CITATION = HEP-LAT 9709134;%%

%\cite{Bernard:1998rm}
\bibitem{Bernard:1998rm}
C.~W.~Bernard {\it et al.},
``Heavy-light decay constants from Wilson and static quarks,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 63} (1998) 362
[arXiv:hep-lat/9709142].
%%CITATION = HEP-LAT 9709142;%%

%\cite{Christensen:1998gm}
\bibitem{Christensen:1998gm}
J.~Christensen, T.~Draper and C.~McNeile,
``Lattice HQET calculation of the Isgur-Wise function,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 63} (1998) 377
[arXiv:hep-lat/9710025].
%%CITATION = HEP-LAT 9710025;%%

%\cite{Bernard:1998hf}
\bibitem{Bernard:1998hf}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Update on the hadron spectrum with two flavors of staggered quarks,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 63} (1998) 215
[arXiv:hep-lat/9710063].
%%CITATION = HEP-LAT 9710063;%%

%\cite{Bernard:1998fg}
\bibitem{Bernard:1998fg}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Light quark spectrum with improved gauge and fermion actions,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 63} (1998) 182
[arXiv:hep-lat/9711013].
%%CITATION = HEP-LAT 9711013;%%

%\cite{Bernard:1997hm}
\bibitem{Bernard:1997hm}
C.~W.~Bernard {\it et al.},
``B mixing on the lattice: f(B), f(B/s) and related quantities,''
arXiv:hep-ph/9709328.
%%CITATION = HEP-PH 9709328;%%

%\cite{Bernard:1998qe}
\bibitem{Bernard:1998qe}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Heavy-light decay constants: MILC results with the Wilson action,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 60A} (1998) 106
[arXiv:hep-lat/9707013].
%%CITATION = HEP-LAT 9707013;%%

%\cite{Bernard:1998qf}
\bibitem{Bernard:1998qf}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Light hadron spectrum: MILC results with the Kogut-Susskind and Wilson  actions,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 60A} (1998) 3
[arXiv:hep-lat/9707014].
%%CITATION = HEP-LAT 9707014;%%


%\cite{Bernard:1997bg}
\bibitem{Bernard:1997bg}
C.~W.~Bernard {\it et al.},
``Exotic hybrid mesons with light quarks,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 53} (1997) 228
[arXiv:hep-lat/9607031].
%%CITATION = HEP-LAT 9607031;%%


%\cite{Christensen:1997sv}
\bibitem{Christensen:1997sv}
J.~Christensen, T.~Draper and C.~McNeile,
``A study of the static-light B(B) parameter,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 53} (1997) 378
[arXiv:hep-lat/9608005].
%%CITATION = HEP-LAT 9608005;%%

%\cite{Bernard:1997yi}
\bibitem{Bernard:1997yi}
C.~W.~Bernard {\it et al.},
``Assorted weak matrix elements involving the bottom quark,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 53} (1997) 374
[arXiv:hep-lat/9608088].
%%CITATION = HEP-LAT 9608088;%%

%\cite{Bernard:1997by}
\bibitem{Bernard:1997by}
C.~W.~Bernard {\it et al.}  [MILC Collaboration],
``Update on f(B),''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 53} (1997) 358
[arXiv:hep-lat/9608092].
%%CITATION = HEP-LAT 9608092;%%

%\cite{Bernard:1997em}
\bibitem{Bernard:1997em}
C.~W.~Bernard {\it et al.},
``Recent MILC spectrum results,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 53} (1997) 212
[arXiv:hep-lat/9608102].
%%CITATION = HEP-LAT 9608102;%%

%\cite{Draper:1996mv}
\bibitem{Draper:1996mv}
T.~Draper and C.~McNeile,
``$B$ Meson Matrix Elements from Various Heavy Quark Effective Theories,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 47} (1996) 429
[arXiv:hep-lat/9509060].
%%CITATION = HEP-LAT 9509060;%%

%\cite{Draper:1995bi}
\bibitem{Draper:1995bi}
T.~Draper, C.~McNeile and C.~Nenkov,
``NRQCD and static systems: A General variational approach,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 42} (1995) 325
[arXiv:hep-lat/9411087].
%%CITATION = HEP-LAT 9411087;%%

%\cite{Draper:1993cx}
\bibitem{Draper:1993cx}
T.~Draper and C.~McNeile,
``An Investigation into a wavelet accelerated gauge fixing algorithm,''
arXiv:hep-lat/9312044.
%%CITATION = HEP-LAT 9312044;%%

%\cite{Draper:1994qj}
\bibitem{Draper:1994qj}
T.~Draper and C.~McNeile,
``Variational calculation of heavy - light meson properties,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 34} (1994) 453
[arXiv:hep-lat/9401013].
%%CITATION = HEP-LAT 9401013;%%

\bibitem{Allton:1992qd}
C.~R.~Allton {\it et al.}  [UKQCD Collaboration],
``First results from the UKQCD Collaboration,''
Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 26} (1992) 211.
%%CITATION = NUPHZ,26,211;%%


\bibitem{McNeile:2000qmt3e}
``Progress in lattice QCD calculations on the T3E,'' Craig McNeile,
Proceedings of the
   Sixth European SGI/Cray MPP workshop. 7 --8 September, Manchester



\end{thebibliography}
